Dear users.
Please be patien on me I'm going do my best to update every problem that is going to be issues!

RELATED
How to Write a Business Letter to a Company
LEARN MORE →
An agreement paper, also known as a letter of agreement, is a paper that summarizes a deal between two or more parties. It is like a contract in that it details the agreement between these parties and all of the logistics involved -- who the parties are, who is providing what services, and who pays whom, when and how much. Agreement letters should be signed and filed as a record by the administrative staff of each company or party involved.


 
Type the phrase “Agreement Letter” or “Agreement Paper” at the top of the page to make clear that this document will detail the agreement between you and your partner parties.

Include the name of your partner company and the company’s address next, as you would in a business letter.

VIDEO OF THE DAY
Brought to you by Techwalla
Brought to you by Techwalla
List the subject of the agreement and the reference number; the reference number is solely for your administrative staff.

Address your letter to the head of your partner company. “Dear X” will suffice.

Write the next section, called “Scope of Work.” This is the section in which you detail the services that you expect from the partner company. Use bullets to outline the exact functions that you expect the company to provide.

Detail the time period of this work in your next section. You can include subsections explaining how often you expect the partner company to report to your company with their progress and how often and how much you will pay this partner company. In this section, you should also include any expenses incurred by the partner company that you expect to cover.

List the administrative staff member that your partner company should contact in the event that there are problems or concerns. This is the final section of your letter.

Sign the letter of agreement and have the relevant people at your partner company sign it as well. Then have your administrative person copy it and send the partner company a copy.

Tip
Keep a copy of this letter of agreement on file with your administrative staff. It is a good idea to keep a copy on a computer and a flash drive, as well as a printed copy just in case anything gets lost or computers crash.

Warning
Keep your letter of agreement specific to your project. If there are extra terms that need to be added to the agreement, add extra sections to your letter.

